On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-16 techreport.tex
Fix the illustration figures.
1. Neater.
2. Fix some rendering problems caused by ps2pdf.

\documentclass[conference]{IEEEtran}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{color}
%\usepackage{epstopdf}

@@

{\color{blue} Before we introduce our main results, we need Lemma \ref{lem:quadratic}, which gives the strategyproof equilibrium for the discrete crowdsensing game. }
\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
\begin{picture}(4,4)(-1.5,-0.5)
\put (-4,1){\vector(1,0){4.2}}% draw x axe
\put (-3,0){\vector(0,1){3.2}} %draw y axe
\qbezier(-1.2,1.6)(-2.15,1.6)(-2.4,-0.2)% draw graph
\qbezier(-1.2,1.6)(-0.25,1.6)(0,-0.2)
\put(-1.2,0){\line(0,1){3.2}} % draw solid lines
\multiput(-2,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dashed lines
\multiput(-1,0)(0,0.2){16}{\line(0,1){0.1}}
\multiput(0,0)(0,0.2){16}{\line(0,1){0.1}}
\put (-1.4,0.6){$\hat{x}$}
\put (-1.0,1){\circle{0.1}}
\put (-0.95,0.6){$\lfloor \hat{x}+\frac{1}{2}\rfloor$}
\put (-2,-0.5){(a)}% lengend

\put (1,1){\vector(1,0){4.2}}% draw x axe
\put (2,0){\vector(0,1){3.2}} %draw y axe
\qbezier(3.2,1.6)(2.25,1.6)(2.0,-0.2)% draw graph
\qbezier(3.2,1.6)(4.15,1.6)(4.4,-0.2)
\put(3.2,0){\line(0,1){3.2}} % draw solid lines
\multiput(3,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dash lines
\multiput(4,0)(0,0.2){16}{\line(0,1){0.1}}
\multiput(5,0)(0,0.2){16}{\line(0,1){0.1}}
\put (3.3,0.6){$\hat{x}$}
\put (3.0,1){\circle{0.1}}
\put (1.8,0.6){$\lceil \hat{x}-\frac{1}{2}\rceil$}
\put (3,-0.5){(b)}% lengend
\end{picture}
\caption{\color{black}Two cases of the parabola symmetric axis. The dashed vertical lines denote $x=k\in\mathbb{Z}$, and each solid vertical line is the symmetric axis of the parabola. Each circled point is the integer closest to the axis.}
\label{fig:quad_prop}
\end{figure}

@@

We next analyze the payment to each user. For the truthfulness, the utility $u_i$ of each user $i$ maximizes at its real cost unit $\kappa_i$ whatever strategies other users take. Based on (\ref{eqn:user_utility_2}), we have
\begin{equation}
\label{eqn:drv_u}
\frac{\partial u_i}{\partial s_i}(\kappa_i) = \frac{\partial p_i}{\partial s_i}(\kappa_i)-\kappa_i \frac{\partial t_i}{\partial s_i}(\kappa_i)=0
\end{equation}
holds for any $\kappa_i\in\mathbb{R}^+$. Usually, for each user, the more cost unit it will suffer, the more reluctant it will be to participate in crowdsensing. If the user would like to be out of the crowdsensing game, it just declares a very large cost unit. As a result, its utility should be 0 in nature. Thus, it is reasonable to assume both the payment $p_i$ and the required sensing time $t_i$ will finally converge to 0: $\lim_{s_i\to+\infty}p_i(s_i)=0$, $\lim_{s_i\to+\infty}t_i(s_i)=0$. Based on this boundary condition and (\ref{eqn:drv_u}), we have\footnote{Here we replace $s_i$ by $s$ to avoid notational confusion.}
\begin{equation}
\int_{s_i}^{+\infty}\frac{\mathrm{d} u_i}{\mathrm{d} s}(s) \mathrm{d}s
=-p_i(s_i)+s_it_i(s_i)+\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s=0,
\end{equation}
which gives the closed-form of $p_i(s_i)$\footnote{Here we choose proper $t_i(s)$ to make the integral $\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s$ converge.}
\begin{equation}
\label{eqn:payment}
p_i(s_i)=s_it_i(s_i)+\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s.
\end{equation}
Thus, the utility of user $i$ is
\begin{equation}
\label{eqn:utility_final}
u_i(s_i)=(s_i-\kappa_i)t_i(s_i)+\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s.
\end{equation}
We discuss the payment $p_i$ and the user utility $u_i$ here in an intuitive way. Figure \ref{fig:truthful_payment} illustrates the geometric relation between payment and user utility. Clearly user utility maximizes at the value $s_i = \kappa_i$ exactly, and the maximum user utility is the area of $ABC$.
\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
\begin{picture}(4.0,4.2)(-2.0,-0.5)
\put (-4,0){\vector(1,0){7.5}}% draw x axe
\put (-4,0){\vector(0,1){3.8}} %draw y axe
\put (-4,3.9){$t_i$}
% give the t curve
\qbezier (-4,3.5)(-2,2)(3.5,0.1)
% give strategy \kappa_i
\put (-1.5,-0.3){$\kappa_i$}
\multiput (-1.5,0)(0,0.2){15}{\line (0,1){0.1}}
\put (-3.1,-0.3){$s_2$}
\multiput (-3.1,0)(0,0.2){15}{\line (0,1){0.1}}
\multiput (-3.0,2.9)(0.2,0){8}{\line (1,0){0.1}}
\put (1.3,-0.3){$s_1$}
\multiput (1.3,0)(0,0.2){5}{\line (0,1){0.1}}
\multiput (-1.4,0.9)(0.2,0){14}{\line (1,0){0.1}}
\put (3.0,-0.3){$s_i$}
% give labels
\put (-4.2,-0.3){$O$}
\put (3.7,-0.1){$B$ $+\infty$}
\put (-1.4, 2.1){$A$}
\put (-1.8, 0.1){$C$}
\put (-1.8, 0.9){$D$}
\put (1.4, 0.9){$E$}
\put (-3.2, 3){$F$}
\put (-1.4, 3){$G$}
\end{picture}
\caption{The relation between user strategy $s_i$ and user utility $u_i$ in the strategyproof crowdsensing incentive mechanism. Here $s_1 > \kappa_i > s_2$. For $s_1$, we have $u_i(s_1)$ is equal to the area of $DEBC$. For $s_2$, we have $u_i(s_2)$ is equal to the area of $ABC$ minus the area of $AFG$. Obviously the area of user utility maximizes at the value $s_i = \kappa_i$.}
\label{fig:truthful_payment}
\end{figure}

@@

\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
\begin{picture}(4,4)(-1.5,-0.5)
\put (-0.5,-0.4){$(x_0,y_0)$}% draw the original point label
\put (-2.5,0){\vector(1,0){5.0}}% draw x axe
\put (2.75,-0.05){$x$}
\put (0,0){\vector(0,1){3.2}} %draw y axe
\put (0,3.35){$y$}
\qbezier(0,0)(-1.25,0)(-2.5,2.8)% draw graph
\qbezier(0,0)(1.25,0)(2.5,2.8)
\put (-1.2,1.5){$u(x,y)>u(x_0,y_0)$}
\put (2,0.6){$u(x,y)<u(x_0,y_0)$}
\put (2,3){$u(x,y)=u(x_0,y_0)$}
\put (2.1,1.5){$\frac{\partial u}{\partial y}(x_0,y_0)>0$}
\put (2.8,2.8){\vector(-1,0){0.3}}
\put (0,0){\vector(1,1){1}}
\put (0,0){\vector(-1,1){1}}
\multiput (1,1)(0,-0.1){10}{\line(0,-1){0.05}}
\multiput (-1,1)(0,-0.1){10}{\line(0,-1){0.05}}
\put (0.9,-0.4){$x_0+\delta$}
\put (-1.8,-0.4){$x_0-\delta$}
\end{picture}
\caption{Local scenario of bivariate function at maximum point of its slice.}
\label{fig:local_bivariate}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{color}
%\usepackage{epstopdf}

@@

{\color{blue} Before we introduce our main results, we need Lemma \ref{lem:quadratic}, which gives the strategyproof equilibrium for the discrete crowdsensing game. }
\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
%\begin{picture}(4,4)(-1.5,-0.5)
%\put (-4,1){\vector(1,0){4.2}}% draw x axe
%\put (-3,0){\vector(0,1){3.2}} %draw y axe
%\qbezier(-1.2,1.6)(-2.15,1.6)(-2.4,-0.2)% draw graph
%\qbezier(-1.2,1.6)(-0.25,1.6)(0,-0.2)
%\put(-1.2,0){\line(0,1){3.2}} % draw solid lines
%\multiput(-2,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dashed lines
%\multiput(-1,0)(0,0.2){16}{\line(0,1){0.1}}
%\multiput(0,0)(0,0.2){16}{\line(0,1){0.1}}
%\put (-1.4,0.6){$\hat{x}$}
%\put (-1.0,1){\circle{0.1}}
%\put (-0.95,0.6){$\lfloor \hat{x}+\frac{1}{2}\rfloor$}
%\put (-2,-0.5){(a)}% lengend
%
%\put (1,1){\vector(1,0){4.2}}% draw x axe
%\put (2,0){\vector(0,1){3.2}} %draw y axe
%\qbezier(3.2,1.6)(2.25,1.6)(2.0,-0.2)% draw graph
%\qbezier(3.2,1.6)(4.15,1.6)(4.4,-0.2)
%\put(3.2,0){\line(0,1){3.2}} % draw solid lines
%\multiput(3,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dash lines
%\multiput(4,0)(0,0.2){16}{\line(0,1){0.1}}
%\multiput(5,0)(0,0.2){16}{\line(0,1){0.1}}
%\put (3.3,0.6){$\hat{x}$}
%\put (3.0,1){\circle{0.1}}
%\put (1.8,0.6){$\lceil \hat{x}-\frac{1}{2}\rceil$}
%\put (3,-0.5){(b)}% lengend
%\end{picture}
\begin{tikzpicture}
\coordinate (xmin1) at (-4,1);
\coordinate (xmax1) at (0.3,1);
\coordinate (ymin1) at (-3,0);
\coordinate (ymax1) at (-3,3);

\draw (xmax1) node [above] {$n_i$};
\draw (ymax1) node [right] {$u_i$};
\draw[-latex] (xmin1)--(xmax1);
\draw[-latex] (ymin1)--(ymax1);
\draw (-1.2,0)--(-1.2,3.2);
\draw[dashed] (-2,0)--(-2,3.2) (-1,0)--(-1,3.2);
\draw (-1,1) circle (1pt);
\draw (-1,1) node [below right] {$\lfloor \hat{x}+\frac{1}{2}\rfloor$};
\draw (-1.2,1) node [below left] {$\hat{x}$};
\draw (-1.2,1.6) parabola (-2.4,-0.2);
\draw (-1.2,1.6) parabola (0,-0.2);

\draw (-2,-0.5) node {(a)};% lengend

\coordinate (xmin2) at (0.8,1);
\coordinate (xmax2) at (4.5,1);
\coordinate (ymin2) at (2,0);
\coordinate (ymax2) at (2,3);

\draw (xmax2) node [above] {$n_i$};
\draw (ymax2) node [right] {$u_i$};
\draw[-latex] (xmin2)--(xmax2);
\draw[-latex] (ymin2)--(ymax2);
\draw (3.2,0)--(3.2,3.2);
\draw[dashed] (3,0)--(3,3.2) (4,0)--(4,3.2);
\draw (3,1) circle (1pt);
\draw (3,1) node [below left] {$\lceil \hat{x}-\frac{1}{2}\rceil$};
\draw (3.2,1) node [below right] {$\hat{x}$};
\draw (3.2,1.6) parabola (2,-0.2);
\draw (3.2,1.6) parabola (4.4,-0.2);

\draw (3,-0.5) node {(b)};% lengend
\end{tikzpicture}
\caption{\color{black}Two cases of the parabola symmetric axis. The dashed vertical lines denote $x=k\in\mathbb{Z}$, and each solid vertical line is the symmetric axis of the parabola. Each circled point is the integer closest to the axis.}
\label{fig:quad_prop}
\end{figure}

@@

We next analyze the payment to each user. For the truthfulness, the utility $u_i$ of each user $i$ maximizes at its real cost unit $\kappa_i$ whatever strategies other users take. Based on (\ref{eqn:user_utility_2}), we have
\begin{equation}
\label{eqn:drv_u}
\frac{\partial u_i}{\partial s_i}(\kappa_i) = \frac{\partial p_i}{\partial s_i}(\kappa_i)-\kappa_i \frac{\partial t_i}{\partial s_i}(\kappa_i)=0
\end{equation}
holds for any $\kappa_i\in\mathbb{R}^+$. Usually, for each user, the more cost unit it will suffer, the more reluctant it will be to participate in crowdsensing. If the user would like to be out of the crowdsensing game, it just declares a very large cost unit. As a result, its utility should be 0 in nature. Thus, it is reasonable to assume both the payment $p_i$ and the required sensing time $t_i$ will finally converge to 0: $\lim_{s_i\to+\infty}p_i(s_i)=0$, $\lim_{s_i\to+\infty}t_i(s_i)=0$. Based on this boundary condition and (\ref{eqn:drv_u}), we have\footnote{Here we replace $s_i$ by $s$ to avoid notational confusion.}
\begin{equation}
\int_{s_i}^{+\infty}\frac{\mathrm{d} u_i}{\mathrm{d} s}(s) \mathrm{d}s
=-p_i(s_i)+s_it_i(s_i)+\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s=0,
\end{equation}
which gives the closed-form of $p_i(s_i)$\footnote{Here we choose proper $t_i(s)$ to make the integral $\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s$ converge.}
\begin{equation}
\label{eqn:payment}
p_i(s_i)=s_it_i(s_i)+\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s.
\end{equation}
Thus, the utility of user $i$ is
\begin{equation}
\label{eqn:utility_final}
u_i(s_i)=(s_i-\kappa_i)t_i(s_i)+\int_{s_i}^{+\infty}t_i(s)\mathrm{d}s.
\end{equation}
We discuss the payment $p_i$ and the user utility $u_i$ here in an intuitive way. Figure \ref{fig:truthful_payment} illustrates the geometric relation between payment and user utility. Clearly user utility maximizes at the value $s_i = \kappa_i$ exactly, and the maximum user utility is the area of $ABC$.
\begin{figure}[!t]
\centering{}
%\setlength{\unitlength}{1cm}
%\begin{picture}(4.0,4.2)(-2.0,-0.5)
%\put (-4,0){\vector(1,0){7.5}}% draw x axe
%\put (-4,0){\vector(0,1){3.8}} %draw y axe
%\put (-4,3.9){$t_i$}
%% give the t curve
%\qbezier (-4,3.5)(-2,2)(3.5,0.1)
%% give strategy \kappa_i
%\put (-1.5,-0.3){$\kappa_i$}
%\multiput (-1.5,0)(0,0.2){15}{\line (0,1){0.1}}
%\put (-3.1,-0.3){$s_2$}
%\multiput (-3.1,0)(0,0.2){15}{\line (0,1){0.1}}
%\multiput (-3.0,2.9)(0.2,0){8}{\line (1,0){0.1}}
%\put (1.3,-0.3){$s_1$}
%\multiput (1.3,0)(0,0.2){5}{\line (0,1){0.1}}
%\multiput (-1.4,0.9)(0.2,0){14}{\line (1,0){0.1}}
%\put (3.0,-0.3){$s_i$}
%% give labels
%\put (-4.2,-0.3){$O$}
%\put (3.7,-0.1){$B$ $+\infty$}
%\put (-1.4, 2.1){$A$}
%\put (-1.8, 0.1){$C$}
%\put (-1.8, 0.9){$D$}
%\put (1.4, 0.9){$E$}
%\put (-3.2, 3){$F$}
%\put (-1.4, 3){$G$}
%\end{picture}
\begin{tikzpicture}
\coordinate (org) at (0,0);
\coordinate (xmax) at (7.5,0);
\coordinate (ymax) at (0,3.8);
\coordinate (s1) at (5.5,0);
\coordinate (s2) at (1,0);
\coordinate (si) at (7,0);
\coordinate (ki) at (2.5,0);
\coordinate (A) at (2.5,2);
\coordinate (D) at (2.5,0.8);
\coordinate (E) at (5.5,0.8);
\coordinate (F) at (1,2.8);
\coordinate (G) at (2.5,2.8);

\draw[-latex] (org)--(xmax);
\draw[-latex] (org)--(ymax); % draw axes
\draw (org) node [below] {$O$}; % draw labels
\draw (xmax) node [right] {$B$ $+\infty$}
	(ymax) node [above] {$t_i$}
	(s1) node [below] {$s_1$}
	(s2) node [below] {$s_2$}
	(si) node [below] {$s_i$}
	(ki) node [below] {$\kappa_i$}
	(A) node [above right] {$A$}
	(ki) node [above left] {$C$}
	(D) node [above left] {$D$}
	(E) node [above right] {$E$}
	(F) node [above] {$F$}
	(G) node [above right] {$G$};
\draw[dashed] (s2)--(F)--(G)--(ki) (D)--(E)--(s1); 
\draw (0,3.5) .. controls (2,2) and (4,1.2) .. (7.5,0.2);
\end{tikzpicture}
\caption{The relation between user strategy $s_i$ and user utility $u_i$ in the strategyproof crowdsensing incentive mechanism. Here $s_1 > \kappa_i > s_2$. For $s_1$, we have $u_i(s_1)$ is equal to the area of $DEBC$. For $s_2$, we have $u_i(s_2)$ is equal to the area of $ABC$ minus the area of $AFG$. Obviously the area of user utility maximizes at the value $s_i = \kappa_i$.}
\label{fig:truthful_payment}
\end{figure}

@@

\begin{figure}[!t]
\centering{}
%\setlength{\unitlength}{1cm}
%\begin{picture}(4,4)(-1.5,-0.5)
%\put (-0.5,-0.4){$(x_0,y_0)$}% draw the original point label
%\put (-2.5,0){\vector(1,0){5.0}}% draw x axe
%\put (2.75,-0.05){$x$}
%\put (0,0){\vector(0,1){3.2}} %draw y axe
%\put (0,3.35){$y$}
%\qbezier(0,0)(-1.25,0)(-2.5,2.8)% draw graph
%\qbezier(0,0)(1.25,0)(2.5,2.8)
%\put (-1.2,1.5){$u(x,y)>u(x_0,y_0)$}
%\put (2,0.6){$u(x,y)<u(x_0,y_0)$}
%\put (2,3){$u(x,y)=u(x_0,y_0)$}
%\put (2.1,1.5){$\frac{\partial u}{\partial y}(x_0,y_0)>0$}
%\put (2.8,2.8){\vector(-1,0){0.3}}
%\put (0,0){\vector(1,1){1}}
%\put (0,0){\vector(-1,1){1}}
%\multiput (1,1)(0,-0.1){10}{\line(0,-1){0.05}}
%\multiput (-1,1)(0,-0.1){10}{\line(0,-1){0.05}}
%\put (0.9,-0.4){$x_0+\delta$}
%\put (-1.8,-0.4){$x_0-\delta$}
%\end{picture}
\begin{tikzpicture}
\coordinate (org) at (0,0);
\coordinate (xmin) at (-2.5,0);
\coordinate (xmax) at (2.5,0);
\coordinate (ymax) at (0,3.2);

\draw[-latex] (xmin)--(xmax);
\draw[-latex] (org)--(ymax);
\draw (org) parabola (2.5,2.8);
\draw (org) parabola (-2.5,2.8);
\draw[-latex] (org)--(1,1);
\draw[-latex] (org)--(-1,1);

\draw[dashed] (1,0)--(1,1) (-1,0)--(-1,1);
\draw (3.3,1.5) node {$\frac{\partial u}{\partial y}(x_0,y_0)>0$}
	(0,1.5) node {$u(x,y)>u(x_0,y_0)$}
	(3.2,0.6) node {$u(x,y)<u(x_0,y_0)$}
	(3.2,3.3) node {$u(x,y)=u(x_0,y_0)$};
\draw[-latex] (3,3)--(2.5,2.8);

\draw (org) node [below] {$(x_0,y_0)$}
	(xmax) node [right] {$x$}
	(ymax) node [above] {$y$}
	(0.5,0) node [below right] {$(x_0+\delta)$}
	(-0.5,0) node [below left] {$(x_0-\delta)$};

\draw (-1,0) circle (1pt) (0,0) circle (1pt) (1,0) circle (1pt);
\end{tikzpicture}
\caption{Local scenario of bivariate function at maximum point of its slice.}
\label{fig:local_bivariate}
\end{figure}
